Hydra Battles and Cie

### 2021-08-17 doc/part-hydras.tex
conversion to Alectryon (to be continued)

\begin{enumerate}
\item The first subgoal is as follows:

\begin{Coqanswer}

  h: Hydrae
  IHh : h_forall (fun h : Hydra => height h < hsize h) h
  ============================
   height (node s) < hsize (node s)

\end{Coqanswer}

This goal is easily solvable, using some arithmetic. We let the reader look at the source.

\item The second subgoal is trivial:

\begin{Coqanswer}

  ============================
    h_forall (fun h : Hydra => height h < hsize h) hnil

\end{Coqanswer}

\begin{Coqsrc}
  reflexivity.
\end{Coqsrc}

\item Finally, the last subgoal is also easy to solve:

\begin{Coqanswer}
  h : Hydra
  h0 : Hydrae
  IHh : height h < hsize h
  IHh0 : h_forall (fun h : Hydra => height h < hsize h) h0
  ============================
   h_forall (fun h1 : Hydra => height h1 < hsize h1) 
                 (hcons h h0)
\end{Coqanswer}

\begin{Coqsrc}
 split;auto. 
Qed.   
\end{Coqsrc}

@@

More generally, we prove the following lemma:

@@

\begin{Coqanswer}
1 subgoal (ID 23)
  m : Hydra -> nat
  Hvar : Hvariant lt_wf free m

  small_h := iota (m big_h) : Hydra
  ============================
  forall i : nat, i <= m (iota i)
\end{Coqanswer}

@@

\begin{Coqanswer}
  i, j : nat
  IHij : forall y : t, y o< (i, j) -> y o<= m (iota y)
  ============================
  (i, j) o<= m (iota (i, j))

\end{Coqanswer}

@@

\begin{Coqsrc}
Lemma plus_not_monotonous_l : exists alpha beta gamma : T1,
    alpha t1< beta /\ alpha + gamma = beta + gamma.
Proof.
  exists 3, 5, omega;  now  compute.
Qed.

Lemma mult_not_monotonous :  exists alpha beta gamma : T1,
      alpha t1< beta /\ alpha * gamma = beta * gamma.
Proof.
  exists 3, 5, omega; now compute.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma succ_is_plus_one (alpha : T1) :  succ alpha = alpha + 1.
Proof.
  induction alpha as [|a IHa n b IHb].
  (* ... *)
\end{Coqsrc}

\subsubsection{Arithmetic on Type \texttt{E0}}

>>>>

The first subgoal is easily solvable, using some arithmetic. We let the reader look at the source. The second and third are
almost trivial.

@@

@@

@@

@@

\input{movies/snippets/T1/notMono}

@@

\input{movies/snippets/T1/succIsPlusOne}

\subsubsection{Arithmetic on type \texttt{E0}}
